Implicit yaddayadda

### 2011-10-21 papers/PLDI2012/implicitization.tex
typo join operator

We also assume a join operator $\sqcap: \abstr{X} \times \abstr{X} \rightarrow \abstr{X}$, with infix notation; in practice, it is generally a least upper bound operation, but we only need it to satisfy $\gamma(\abstr{x}) \cup \gamma(\abstr{y}) \subseteq \gamma(\abstr{x} \sqcap \abstr{y})$ for all $\abstr{x},\abstr{y}$.

@@

>>>>

We also assume a join operator $\sqcup: \abstr{X} \times \abstr{X} \rightarrow \abstr{X}$, with infix notation; in practice, it is generally a least upper bound operation, but we only need it to satisfy $\gamma(\abstr{x}) \cup \gamma(\abstr{y}) \subseteq \gamma(\abstr{x} \sqcup \abstr{y})$ for all $\abstr{x},\abstr{y}$.

@@

In order to compare the various techniques, we compare by inclusion the obtained
abstract values at each control points in $P_R$.

\subsection{Precision of the various techniques}

\subsection{Precision of Abstract Domains}
